---
title: "Package: anemia"
author: "Alan Brookhart"
date: "1/22/2017"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## NHANES anemia data

This package builds the example National Health and Nutritional Examination Survey (NHANES) dataset containing data about
anemia and iron status from the years on n=3,990 patients from 1999-2000.  The file was created by merging demographic data with complete blood count file, and nutritional biochemistry lab file.


## Installation

You can install the package from Bitbucket

```{r bb-installation, eval = FALSE}
library("devtools")
devtools::install_bitbucket("novisci/anemia")
```

## Codebook 

* age = age in years of participant (years)
* sex = sex of participant (Male vs Femal)
* tsat = transferrin saturation (%)
* iron = total serum iron (ug/dL)
* hgb = hemoglobin concentration (g/dL)
* ferr = serum ferritin (mg/mL)
* folate = serum folate (mg/mL)
* race = paricipant race (Hispanic, White, Black, Other)
* rdw = red cell distribution width (%)
* wbc = white blood cell count (SI)
* anemia = indicator variable for anemia (according to WHO definition)

## Notes

805 participants with missing observations are dropped.  These can be recovered using the raw data.

NHANES sampling weights are not included.

## To do

Add documentation to file.
